---
title: "Recaman's Sequence Background"
author: "Jordan Winemiller"
date: "17 August 2022"
output:
  html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_packages, warning=FALSE, results='hide', message=FALSE, include=FALSE}
ip = installed.packages()[, 1]
ip = names(unlist(ip))

required_packages = c(
  "grid",
  "png",
  "tidyverse")

for (package in required_packages) {
  if (package %in% ip) {
    next
  } else {
    install.packages(package, repos = "http://cran.us.r-project.org")
  }
}

lapply(required_packages, require, character.only = TRUE)
```

## Creating the dataset

### Creating Recaman's sequence

```{r warning=FALSE, message=FALSE}
make_sequence <- function(num) {
  seq <- numeric(num)
  for (i in 1:length(seq)) {
    curr <- seq[i] - i
    if (curr > 0 & !(curr %in% seq)) {
      seq[i + 1] <- curr
    }
    else
      seq[i + 1] <- seq[i] + i
  }
  seq <- seq[-length(seq)]
  seq
}
```


### Sequence validation

```{r}
test_sequence = make_sequence(15)
test_sequence
```


### Constructing arc

```{r}
construct_arc_color <- function(start, stop, arc_type, arc_color) {
  r <- abs(start - stop) / 2
  x_0 <- min(c(start, stop)) + r
  y_0 <- 0
  switch(
    arc_type,
    "up_forward" = theta <- seq(pi, 0, -0.01),
    "up_backward" = theta <- seq(0, pi, 0.01), 
    "down_forward" = theta <- seq(pi, 2 * pi, 0.01),
    "down_backward" = theta <- seq(2 * pi, pi, -0.01), 
  )
  x <- r * cos(theta) + x_0 
  y <- r * sin(theta) + y_0
  df <- data.frame(x, y, arc_color)
}
```


### Create arc dataset

```{r}
create_visual_df <- function(num, line_size = 1, alpha = 0.9) {
  seq <- make_sequence(num = num)
  initial_df <- data.frame(
    start = seq,
    stop = lead(seq), 
    arc_side = rep_len(c("down_", "up_"), length(seq))
  ) %>% 
  dplyr::mutate(
    arc_direction = ifelse(
      stop - start > 0,
      "forward",
      "backward"),
    arc_type = paste0(arc_side, arc_direction),
    arc_color = case_when(
      arc_type == "down_forward" ~ "blue",
      arc_type == "up_backward" ~ "blue",
      arc_type == "down_backward" ~ "gold",
      arc_type == "up_forward" ~ "gold",
    )
  ) %>% 
  dplyr::filter(!is.na(stop))
  arc_coord_df <- Map(
    construct_arc_color,
    start = initial_df$start,
    stop = initial_df$stop,
    arc_type = initial_df$arc_type,
    arc_color = initial_df$arc_color
  )  
  visual_df <- do.call("rbind", arc_coord_df)
}
```


### Color visualization dataset validation

#### Coordinate point validation

```{r}
test_df = create_visual_df(15)
head(test_df, 5)
```


#### Color assigment validation

```{r}
unique(test_df$arc_color)
```



```{r include=FALSE}
# n = 1986
# vis_df = create_visual_df(1986)
# vis_max_x_lim = 7150
# n = 86
vis_df = create_visual_df(86)
vis_max_x_lim = 230
# n = 36
# vis_df = create_visual_df(36)
# vis_max_x_lim = 120

```


## Create Visualization

### Set visualization parameters

```{r}
vis_df = create_visual_df(86)

vis_size = 1
vis_alpha = 0.7
vis_color = "#4169E1"
vis_max_x_lim = 230
```


### Recaman's sequence visualization one color

```{r}
ggplot(vis_df, aes(x, y)) +
  geom_path(alpha = vis_alpha, linewidth = vis_size, col = vis_color) +
  coord_fixed() +
  xlim(0, vis_max_x_lim) +
  theme(
    plot.background = element_rect(fill = "transparent"),
    panel.border = element_blank(),
    panel.background = element_rect(fill = "transparent"),
    panel.grid = element_blank(),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  ) 
```


### Recaman's sequence visualization one color

```{r}
ggplot(vis_df, aes(x, y, color = as.character(arc_color))) +
  geom_path(alpha = vis_alpha, linewidth = vis_size) +
  scale_color_identity() +
  coord_fixed() + 
  xlim(0, vis_max_x_lim) +
  theme(
    plot.background = element_rect(fill = "#404040"),
    panel.background = element_rect(fill = "#404040"),
    panel.grid = element_blank(),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  ) 
```


## Applying custom background to visual

### Load background image

```{r}
img_path = "./wall.png"
img = png::readPNG(img_path)
```


### Convert to rasterGrob

```{r}
bg_img = rasterGrob(
  img,
  width = unit(1, "npc"),
  height = unit(1, "npc"),
  interpolate = FALSE)
```


### Set visualization parameters

```{r}
bg_vis_df = create_visual_df(86)

bg_vis_size = 0.75 
bg_vis_alpha = 0.9
bg_vis_color = "#4169E1"
bg_vis_max_x_lim = 230
```


### Visualization with background image

```{r}
ggplot(bg_vis_df, aes(x, y)) +
  annotation_custom(bg_img, -Inf, Inf, -Inf, Inf) +
  geom_path(alpha = bg_vis_alpha, linewidth = bg_vis_size, col = bg_vis_color) +
  coord_fixed() +
  xlim(0, bg_vis_max_x_lim) +
  theme(
    plot.background = element_rect(fill = "transparent"),
    panel.border = element_blank(),
    panel.background = element_rect(fill = "transparent"),
    panel.grid = element_blank(),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank()
  ) 
```
